Practical Optional Types for Clojure

### 2015-12-31 metatheory.tex
error values

We prove type soundness following \cite{TF10}.  Our model is extended
to include errors and a \wrong{} value, and we prove well-typed
programs do not go wrong; this is therefore a stronger theorem than
proved by \cite{TF10}.

>>>>

We prove type soundness following Tobin-Hochstadt and Felleisen~\cite{TF10}.  Our model is extended
to include errors \errorvalv{} and a \wrong{} value, and we prove well-typed
programs do not go wrong; this is therefore a stronger theorem than
proved by Tobin-Hochstadt and Felleisen~\cite{TF10}. 
Errors behave like Java exceptions---they can be thrown and propagate ``upwards'' in the evaluation rules
(\errorvalv{} rules are deferred to the appendix).
